Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: significant improvement in the dark energy figure of merit

### 2017-07-13 Draft/Draft0.9.tex
minor changes

\title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: 
constraining the linear evolution of dark energy}

@@

\begin{abstract}
We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
and reduces the area of $w_0-w_a$ contour by 50\%.
The AP method can be combined with the standard BAO method,
greatly increasing the power of ongoing and future galaxy surveys in probing dark energy, 
improving the figure of merit constraints on $(w_0,w_a)$ by a factor of 2. 
\end{abstract}

@@

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space, produces residual geometric distortions in the resultant galaxy distribution, see  Fig.\ref{fig_xy}. 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

In an effort to minimise RSD contamination, the shape of void regions\cite{Ryden1995,LavausWandelt1995}  has been 
proposed as an AP probe. This approach has the advantage that the void regions are easier to model compared with dense regions, but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.

@@

Previously, we proposed to use the  {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect. The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence
(as an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
when incorrect cosmologies are used to infer distances).
In a later work\cite{Li2015}, we developed an AP methodology 
that utilises the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

@@

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
Especially, the DETF figure of merit (FoM) is defined the reciprocal of the area of the error
ellipse enclosing the 95\% confidence limit in the $w_0–w_a$ plane. 
This quantity quantifies the progress in measuring the properties of dark energy.
Larger FoM indicates greater accuracy.
Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=6.5cm]{fig_nbar.eps}
   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Spliting the SDSS galaxies into six redshiftbins, and measuring the correlation function.
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed.
%\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalise these {\em clustering shells} as 
$\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
to nullify the amplitude information of the clustering signal, 
which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.

The right panel of Fig.\ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
The contour lines are not horizontal due to the effects of peculiar velocity,
and the RSD effect clearly manifest itself through the tilting of contour lines.
However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimising the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects:
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.

Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \cite{HR4},
an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
initial redshift $z_{i}=100$, and WMAP5\citep{komatsu2011} cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are adequately corrected \citep{Hartlap,Percival2014}.

@@

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=6cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
   \includegraphics[height=6cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_con}
   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
   %Results are consistent with $\Lambda$CDM.
   The constrained area is significantly reduced after combined with the AP method.
   %This shows the power of the AP method in constraining dynamical dark energy.
   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
   }
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=16cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the results.
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from Horizon Run 4 simulations, 
   and covariance estimated using 2,000 MultiDark PATCHY mocks.
   When altering these options, the results remain robust (black contours).
   }
\end{figure*}

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ km/s/Mpc \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
\begin{eqnarray}
 \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
 w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
 w_a &=& -0.38 \pm 0.41.
\end{eqnarray}
%To derive the constraints combined with our AP method,
%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
%This enables us investigating the redshift evolution of anisotropic clustering.
%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
%and used a $\chi^2$ function to assess the redshift dependence.
%(see Methods for further explanations).
After adding the log-likelihoods of the Planck team sample with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
\begin{eqnarray}
\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
w_0 &=& -1.042 \pm 0.067, \\ \nonumber
w_a &=& -0.07 \pm 0.29.
\end{eqnarray}
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
Adding our new AP constraints significantly reduces the allowable parameter space. 
This can also be visualised as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
This constitutes a significant increase in the figure of merit (FoM)  constraints on $(w_0, w_a)$. This doubling of the FoM($w_o,w_a$) comes at no additional cost or alteration to survey design, thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.

We performed a thorough test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} 
of the systematic correction could influence the final result.

@@

The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

The presented method of clustering shells can be applied to many large spectroscopic galaxy surveys. 
We show that figure of merit constraints on  $(w_0, w_a)$ can be increased by a factor of 2 when considering the small scale clustering shells information in combination with existing constraints. The analysis we perform requires no change to the typical survey strategy of large cosmological redshift surveys, thus we can increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
We expect this approach will play an important role in helping us unveiling the mystery of dark energy.

\begin{acknowledgments}
We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.
\end{acknowledgments}

@@

@@

\bibitem{Hartlap}%[Hartlap et al.(2006)]
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

>>>>

\title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: 
significant improvement in the dark energy figure of merit}

@@

\begin{abstract}
We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
The AP method can %be combined with the standard BAO method,
greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space
produces residual geometric distortions in the resultant galaxy distribution (see  Fig.\ref{fig_xy}). 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

In an effort to minimize RSD contamination, the shape of void regions\cite{Ryden1995,LavausWandelt1995}  has been 
proposed as an AP probe. This approach has the advantage that the void regions are easier to model compared with dense regions, but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.

@@

Previously, we proposed to use the {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect. The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence
(as an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance (i.e., redshift) 
when incorrect cosmologies are used to infer distances).
In a later work\cite{Li2015}, we developed an AP methodology 
that utilizes the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

@@

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
The constraining power is usually quantified by the DETF (Dark Energy Task Force) \cite{DETF} figure of merit, 
defined as the reciprocal of the area of the error ellipse enclosing the 95\% confidence limit (CL) in the $w_0-w_a$ plane. 
Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=6.5cm]{fig_nbar.eps}
   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function.
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed.
%\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalize these {\em clustering shells} as 
$\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
to nullify the amplitude information of the clustering signal, 
which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.

The right panel of Fig.\ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
The contour lines are not horizontal due to the effects of peculiar velocity,
and the RSD effect clearly manifest itself through the tilting of contour lines.
However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects:
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.

Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \cite{HR4},
an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
initial redshift $z_{i}=100$, and WMAP5\citep{komatsu2011} cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
(mainly comes from redshift evolution of RSD and galaxy bias)
reaches 4-6\% at the highest redshift bin,
and is minor ($\lesssim2\%$) at the other redshift bins.
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are adequately corrected \citep{Hartlap,Percival2014}.

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_con}
   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
   %Results are consistent with $\Lambda$CDM.
   The constrained area is significantly reduced after combined with the AP method.
   %This shows the power of the AP method in constraining dynamical dark energy.
   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
   }
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=14cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the results.
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from Horizon Run 4 simulations, 
   and covariance estimated using 2,000 MultiDark PATCHY mocks.
   When altering these options, the results remain robust (black contours).
   }
\end{figure*}

@@

%It should be mentioned that simply using a linear interpolation to infer the values of $\xi$ in a new cosmology does {\it not} work.
%The interpolation introduces an artificial smoothing in the inferred $\xi$, and reduces the

@@

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ km/s/Mpc \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
%\begin{eqnarray}
% \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
% w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
% w_a &=& -0.38 \pm 0.41.
%\end{eqnarray}
\small
\begin{equation}
 \Omega_m = 0.309 \pm 0.010,\
 w_0 = -0.938 \pm 0.109,\
 w_a = -0.38 \pm 0.41.
\end{equation}
\normalsize
%To derive the constraints combined with our AP method,
%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
%This enables us investigating the redshift evolution of anisotropic clustering.
%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
%and used a $\chi^2$ function to assess the redshift dependence.
%(see Methods for further explanations).
After adding the log-likelihoods of the Planck team sample with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
%\begin{eqnarray}
%\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
%w_0 &=& -1.042 \pm 0.067, \\ \nonumber
%w_a &=& -0.07 \pm 0.29.
%\end{eqnarray}
\small
\begin{equation}
 \Omega_m = 0.301 \pm 0.008,\
 w_0 = -1.042 \pm 0.067,\
 w_a = -0.07 \pm 0.29.
\end{equation}
\normalsize
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

The marginalized constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
Adding our new AP constraints significantly reduces the allowable parameter space. 
This can also be visualized as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
This constitutes a significant increase in the figure of merit constraints on $(w_0, w_a)$. 
This doubling of the figure of merit comes at no additional cost or alteration to survey design, 
thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.

We performed a thorough test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The result does not change significantly if we remove the highest redshift bin,
where the estimated systematics is comparably large.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} 
of the systematic correction could influence the final result.

@@

The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modeling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller clustering scales, allowing for the inclusion of more $k$-modes and hence more information.

We believe that the presented method of clustering shells will be applied to many spectroscopic galaxy surveys. 
The current figure of merit constraints on $(w_0, w_a)$ is increased by a factor of 2 
when considering the small scale clustering shells information in combination with existing constraints. 
The analysis we perform requires no change to the typical survey strategy of large cosmological redshift surveys, 
thus we can increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
We expect this approach will play an important role in helping us unveiling the mystery of dark energy.

\

\begin{acknowledgments}
We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.

Based on observations obtained with Planck (http://www.esa.int/Planck), 
an ESA science mission with instruments and contributions directly funded by 
ESA Member States, NASA, and Canada.

Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the
National Science Foundation, and the U.S. Department of Energy Office of Science. 
The SDSS-III web site is http://www.sdss3.org/. 
SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions
of the SDSS-III Collaboration.
\end{acknowledgments}

@@

\bibitem{DETF}
Albrecht, A., Bernstein, G., \& Cahn, R., et al. [astro-ph/0609591].

@@

\bibitem{Hartlap}%[Hartlap et al.(2006)]
Hartlap, J., Simon, P., \& Schneider, P. [astro-ph/0608064].
